---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fractaltree

The goal of fractaltree is to plot trees as fractals. Using the shape of a single "leaf", every subsequent growht takes the same shape.

```{r, message=FALSE, echo=FALSE}
library(fractaltree)
library(magrittr)
library(dplyr)

leaf <- local({
  matrix(
    c(0, 0, 0, 1,
      0, 0.45, 0.2, 1,
      0, 0.45, -0.2, 1),
    byrow = TRUE, ncol = 4
  )
})

tree <- fractal_tree(leaf, depth = 3, growth_fraction = 1)

tree %>% 
  filter(i <= 1) %>% 
  bind_rows(
    tree %>% 
      filter(i <= 2) %>% 
      translate(c(1.5, 0))
  ) %>% 
  bind_rows(
    tree %>% 
      filter(i <= 4) %>% 
      translate(c(4, 0))
  ) %>%  
  plot_tree()

```

## Installation


```r
devtools::install_github("andrie/fractaltree")
```

## Example

You can use the `depth` argument to change the number of growth cycles, and the `shrinkage_factor` to control how much growth with every generation.  If the growth is high, the resulting image may resemble a shrub, and if the growth is low, the resulting image may resemble a mature tree.

```{r, fig.keep='all'}
fractal_tree(leaf, depth = 5, growth_fraction = 1) %>% 
  plot_tree()

fractal_tree(leaf, depth = 5, growth_fraction = 0.75) %>% 
  plot_tree()

fractal_tree(leaf, depth = 5, growth_fraction = 0.5) %>% 
  plot_tree()


```

You can make interesting tree shapes if the leaf shape is asymmetric:

```{r}
leaf <- local({
  matrix(
    c(0, 0, 0, 1,
      0, 0.45, 0.12, 0.80,
      0, 0.85, -0.04, 0.95),
    byrow = TRUE, ncol = 4
  )
})

leaf %>% 
  fractal_tree(depth = 1) %>% 
  plot_tree()

leaf %>% 
  fractal_tree(depth = 7, growth_fraction = 0.6) %>% 
  plot_tree()

```

## Translate, rotate and grow

You can use the functions `translate()`, `rotate()` and `shrink()` to perform spatial transformation on a tree.

## Kaleidoscope

In addition you can use the `kaleidoscope()` function to turn a tree into a symmetric diagram:

```{r}
leaf %>% 
  fractal_tree(depth = 3, growth_fraction = 0.8) %>% 
  kaleidoscope() %>% 
  plot_tree(colors = c( "red", "blue"))

```

By first translating a tree in 2-dimensional space, using the `translate()` function, you can create very interesting `kaleidoscope()` images:

```{r}
leaf %>% 
  fractal_tree(depth = 3, growth_fraction = 0.8) %>% 
  kaleidoscope() %>% 
  translate(c(0, 5)) %>% 
  kaleidoscope() %>% 
  plot_tree(colors = c( "red", "blue"))

```
